Random Generation of Rich \\ Abstract Data Type Values

### 2019-02-06 paper/relatedwork.tex
Minor fixes

%
% Boltzmann models
%
Boltzmann models \cite{Duchon2004} are a general approach to randomly generating
combinatorial structures such as trees and graphs, closed simply-typed lambda
terms, etc.
%
A random generator built around such models uniformly generates values of a
target size with a certain size tolerance.
%
However, it has been argued that this approach has theoretical and practical
limitations in the context of software testing \cite{feldt2013}.
%
In a recent work, Bendkowski provides a framework called \emph{boltzmann-brain}
to specify and synthesize standalone Haskell random generators based on
Boltzmann models \cite{bendkowski2018}.
%
This framework mixes parameter tuning and rejection of unwanted samples to
approximate the desired distribution of values according to user demands.
%
In this approach, the overall discard ratio depends on how constrained the
desired distribution is.
%
On the other hand, our work is focused on approximating the desired distribution
as much as possible via parameter optimization, without discarding any generated
value at runtime.
%
Although promising, we found several difficulties to compare both approaches in
practice due that \emph{boltzmann-brain} is considered a standalone utility that
produces self-contained samplers.
%
In this light, data specifications have to be manually written using a special
syntax, and cannot include Haskell ground types like |String| or |Int|,
difficulting the integration of this tool to existing Haskell codebases like the
ones we consider in this work.

>>>>

%
% Boltzmann models
%
Boltzmann models \cite{Duchon2004} are a general approach to randomly generating
combinatorial structures such as trees and graphs, closed simply-typed lambda
terms, etc.
%
A random generator built around such models uniformly generates values of a
target size with a certain size tolerance.
%
However, it has been argued that this approach has theoretical and practical
limitations in the context of software testing \cite{feldt2013}.
%
In a recent work, Bendkowski et al. provides a framework called
\emph{boltzmann-brain} to specify and synthesize standalone Haskell random
generators based on Boltzmann models \cite{bendkowski2018}.
%
This framework mixes parameter tuning and rejection of samples of unwanted sizes
to approximate the desired distribution of values according to user demands.
%
The overall discard ratio then depends on how constrained the desired sizes of
values are.
%
On the other hand, our work is focused on approximating the desired distribution
as much as possible via parameter optimization, without discarding any generated
value at runtime.
%
Although promising, we found difficulties to compare both approaches in practice
due that \emph{boltzmann-brain} is considered a conceptual standalone utility
that produces self-contained samplers.
%
In this light, data specifications have to be manually written using a special
syntax, and cannot include Haskell ground types like |String| or |Int|,
difficulting the integration of this tool to existing Haskell codebases like the
ones we consider in this work.
